Computing Exact Restricted Isometry Constants via\\ Mixed Integer Semidefinite Programming

### 2016-03-14 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
explain numerical results in contrast to Asp08 in more detail

  Let $\check{X}$ be an extreme point of \eqref{Proj} (since the set of
  optimal points of~\eqref{Proj} is a nonempty, convex, and compact, such a
  point exists, see~\cite[Corollary 18.5.1]{Roc70}). Defining the face $F =
  \{\check{X}\}$ and applying Theorem~\ref{patakiLemma} on \eqref{Proj}
  gives
  \begin{equation*}
    \tfrac{1}{2} \Rk(\check{X}) \cdot (\Rk(\check{X})+1) \leq \tilde{m} + dim(F) = 1 + 0 = 1,
  \end{equation*}
  since there are $\tilde{m} = 1$ linear constraints. Since $\check{X} = 0$
  is infeasible for $\Tr(X) = 1$, it follows that $\Rk(\check{X}) = 1$,
  which can then be lifted to an optimal solution of \eqref{MISDP} of rank
  one.
\end{proof}

@@

The continuous SDPs are solved using the command-line version of
SDPA~7.3.8. We compute the left- and right-hand restricted isometry
constant $\alpha_k$ and $\beta_k$ either exactly using~\eqref{MISDP} or
produce corresponding bounds via \eqref{Asp07} and \eqref{Asp08Dual}. In
the latter case, we solve 15 SDPs for $\rho$ between~$0$ and the maximum
diagonal entry of $A\T A$.\comment{As done in \cite{Asp08}?}

>>>>

  Let $\check{X}$ be an extreme point of \eqref{Proj} (since the set of
  optimal points of~\eqref{Proj} is nonempty, convex, and compact, such a
  point exists, see~\cite[Corollary 18.5.1]{Roc70}). Defining the face $F =
  \{\check{X}\}$ and applying Theorem~\ref{patakiLemma} on \eqref{Proj}
  gives
  \begin{equation*}
    \tfrac{1}{2} \Rk(\check{X}) \cdot (\Rk(\check{X})+1) \leq \tilde{m} + dim(F) = 1 + 0 = 1,
  \end{equation*}
  since there are $\tilde{m} = 1$ linear constraints. Since $\check{X} = 0$
  is infeasible for $\Tr(X) = 1$, it follows that $\Rk(\check{X}) = 1$,
  which can then be lifted to an optimal solution of \eqref{MISDP} of rank
  one.
\end{proof}

@@

The continuous SDPs are solved using the command-line version of
SDPA~7.3.8. We compute the left- and right-hand restricted isometry
constant $\alpha_k$ and $\beta_k$ either exactly using~\eqref{MISDP} or
produce corresponding bounds via \eqref{Asp07} and \eqref{Asp08Dual}. In
the latter case, we solve 15 SDPs for $\rho$ between~$0$ and the maximum
diagonal entry of $A\T A$. This is the same approach as in \cite{Asp08},
except that we reduced the number of problems from 25 to 15, as this did
not seem to influence the quality of th solutions much in our preliminary
experiments but brought the solving times more in line with the other
approaches.
